Manuscript progress report

### 2023-12-02 Docs/manuscript.Rmd
data application outcome, with problems

>>>>

```{r fig_pred_anhanes}
rand_id2 <- sample(unique(nhanes_pred_fgfpca$id), 4)

fig_fgfpca_nhanes <- nhanes_pred_fgfpca %>% 
  filter(id %in% rand_id2) %>%
  mutate_at(vars(starts_with("pred")), function(x){exp(x)/(1+exp(x))}) %>%
  rename(t=sind) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=pred240, col = "4am"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred480, col = "8am"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred720, col = "12pm"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred960, col = "4pm"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred1200, col = "8pm"), linetype="dashed", na.rm=T)+
  facet_wrap(~id)+
  labs(title = "fGFPCA", col = "Maximum observation time")+
  scale_x_continuous(breaks = window3, 
                     labels = c("Midnight", "4am", "8am", "12pm", "4pm", "8pm", "Midnight"))
```

```{r}
fig_adglmm_nhanes <- nhanes_pred_adglmm %>% 
  filter(id %in% rand_id2) %>%
  mutate_at(vars(starts_with("pred")), function(x){exp(x)/(1+exp(x))}) %>%
  mutate(t = t*1440) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=pred240, col = "4am"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred480, col = "8am"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred720, col = "12pm"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred960, col = "4pm"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred1200, col = "8pm"), linetype="dashed", na.rm=T)+
  facet_wrap(~id)+
  labs(title = "GLMMadaptive", col = "Maximum observation time")+
  scale_x_continuous(breaks = window3, 
                     labels = c("Midnight", "4am", "8am", "12pm", "4pm", "8pm", "Midnight"))
```

```{r}
ggarrange(fig_fgfpca_nhanes, fig_adglmm_nhanes, nrow = 1, common.legend = T)
```

## Issues

In step 4 of fGFPCA, some eigenvalues, after re-evaluation, was very, very small. It also lost its monotone decreasing nature.

The debias step of fGFPCA also took a very, very long time.
